Wide binaries in Gaia DR1

### 2016-09-28 paper/ms.tex
started writing some of hte marginalization down

>>>>

\appendix

Here we derive analytic expressions for the marginal likelihood integrals above.

\todo{Hypothesis 1}

The integrals for Hypothesis 2 are somewhat easier because the true velocity
vector can be considered to be already in the orthogonal basis defined by the
tangent plane at the coordinates of the source (we are assuming an isotropic
velocity prior). We will analytically integrate over the velocity components
$(v_\alpha,v_\delta,v_r)$ and leave the distance integral to be done
numerically:
\begin{equation}
  \int \, \dd^3\bs{v} \, L(\bs{v}, d) \, p(\bs{v})
\end{equation}
The covariance matrix over parallax, proper motion components, and
radial velocity (if they exist) is $\matrx{C}$ and the inverse variance matrix
is $\matrx{V}$. Defining the constant
\begin{equation}
  \mathcal{Z} = \left[ \det \left(\frac{\matrx{V}}{2\pi} \right) \right]^{1/2}
\end{equation}
the integrand can be written
\begin{equation}
  L(\bs{v}, d) \, p(\bs{v}) = \mathcal{Z} \,
    \exp \left[ -\frac{1}{2} \transp{\left(\bs{x} - \bs{x}_\theta \right)} \,
    \matrx{V} \,
    \left(\bs{x} - \bs{x}_\theta \right)
    - \frac{|\bs{v}|^2}{2\,\sigma^2} \right] \\
\end{equation}
